More straightforward movement variable definitions

### 2024-02-07 scripts/01.1_categorizeMovement.qmd
re-ran movement vars and saved the output

# Create a dataset with all seasons combined
allMovementBehavior <- purrr::list_rbind(movementBehavior)
movementBehaviorScaled <- allMovementBehavior %>%
  mutate(across(-c(Nili_id, seasonUnique, birth_year, sex, dataset, 
                   homeRange, coreArea, coreAreaFidelity), # not scaling the space use params, because I'm not putting those into a PCA.
                function(x){as.numeric(as.vector(scale(x)))}))
```

@@

```{r}
#| include: false
demo <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, daysTracked, propDaysTracked, dataset, birth_year, sex)
space_use <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, coreArea, homeRange, coreAreaFidelity)
movement <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, mnDailyMnAlt, meanDFD, meanDMD, meanDDT, mnTort)
roost_behavior <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, propSwitch, shannon, uniqueRoosts)
```

@@

>>>>

# Create a dataset with all seasons combined
allMovementBehavior <- purrr::list_rbind(movementBehavior)
movementBehaviorScaled <- allMovementBehavior %>%
  mutate(across(-c(Nili_id, seasonUnique, birth_year, sex, homeRange, coreArea, coreAreaFidelity), # not scaling the space use params, because I'm not putting those into a PCA.
                function(x){as.numeric(as.vector(scale(x)))}))
```

@@

```{r}
#| include: false
demo <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, daysTracked, propDaysTracked, birth_year, sex)
space_use <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, coreArea, homeRange, coreAreaFidelity)
movement <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, mnDailyMnAlt, meanDFD, meanDMD, meanDDT, mnTort)
roost_behavior <- movementBehaviorScaled %>%
  dplyr::select(Nili_id, seasonUnique, propSwitch, shannon, uniqueRoosts)
```

@@

```{r}
head(red)
new_movement_vars <- red
save(new_movement_vars, file = here::here("data", "new_movement_vars.Rda"))
```
